Contracts for unions and intersections are hard for Nickel

### 2021-05-31 paper.tex
Rework the plan section

We will use the syntax of Nickel to write most examples throughout this paper.
Syntactically, Nickel looks like a simple ML language with records. \nickel{let
id = value in exp} is used to bind a value to an identifier in an expression.
Functions are declared using the \nickel{fun arg1 ... argn => body} syntax. List
are written as \nickel{[x1, ..., xn]} and records as \nickel{\{ field1 = value1,
..., fieldn = valuen \}}. Some examples uses constructions that are not
currently available in Nickel for illustration purpose: in particular, we will
use \nickel{A & B} (resp.  \nickel{A | B}) for the intersection (resp. union) of
contracts (or types) \nickel{A} and \nickel{B}.

@@

\subsection*{Structure of this paper}
This paper is structured as follows, Section \ref{sec:intro} introduces
this paper; Section \ref{sec:feat-lang} outlines various features
of programming languages that may interact badly with union and intersection
contracts.
Section \ref{sec:union-inter} gives a primer on Unions and Intersections,
enough to understand this work.

Section \ref{sec:issues-sem} shows what difficulties or issues, proper of
unions and intersections, one may
encounter when trying to develop a union and intersection contracts.
Section \ref{sec:issues-literature} presents issues and shortcomings found
in existing attempts to solve this problem.
Section \ref{sec:related-work} provides some related work, and Section
\ref{sec:conclusion} concludes.

>>>>

We will use the syntax of Nickel to write most examples throughout this paper.
Syntactically, Nickel looks like a simple ML language with records. \nickel{let
id = value in exp} is used to bind a value to an identifier in an expression.
Functions are declared using the \nickel{fun arg1 ... argn => body} syntax. List
are written as \nickel{[x1, ..., xn]} and records as \nickel{\{ field1 = value1,
..., fieldn = valuen \}}. Some examples uses constructions that are not
currently available in Nickel for illustration purpose: in particular, we will
use \nickel{A & B} (resp.  \nickel{A | B}) for the intersection (resp. union) of
contracts (or types) \nickel{A} and \nickel{B}. Finally, we will write
\nickel{exp @ C}\footnote{The current Nickel implementation actually uses the
syntax \nickel{exp | C} for contract application, but we rather keep \nickel{|}
for unions here}  for the application of a contract \nickel{C} to the expression
\nickel{exp}.

@@

\subsection*{Structure of this paper}
Section~\ref{sec:intro} introduced the perspective of designing a configuration
language. We presented the concept of contracts and detailed why contracts are
particularly fitted for a configuration language, and more generally for data
validation or program correctness in a dynamically typed language. The rest of
the paper is structured as follows:
\begin{itemize}
    \item Section~\ref{sec:feat-lang} outlines various common features of
        programming languages that may interact in a bad way with union and
        intersection contracts.
    \item Section~\ref{sec:union-inter} introduces unions and intersections and
        lists the possible motivations for adding them to a language.
    \item Section~\ref{sec:issues-sem} studies intrinsic difficulties one may
        encounter when trying to implement union and intersection contracts in
        practice.
    \item Section~\ref{sec:issues-literature} presents the shortcomings found in
        existing attempts to solve said difficulties.
    \item Section~\ref{sec:related-work} provides some related work.
\end{itemize}

Section~\ref{sec:conclusion} concludes the paper.
